Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-06-20 template.tex
just trudging along not getting the Laplacian of the Dawson

Let $u = x-y$, so that $du = -dy$ and note that $D(x)$ is an odd function.  The substitution gives

@@

r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) - z\int_{0}^{\infty} e^{zu} D(u-x) du \right)

@@

The integral is the Laplace transform of the shifted Dawson function, evaluated at $-z$.

>>>>

Let $u = x-y$, $z=-k$, and note that $D(x)$ is an odd function.  These substitutions give

@@

r_a(t) * \Im\lbrace s_a(t) \rbrace = \\ \frac{2}{\sqrt{\pi}} R_0 E_0 \sigma_t^2 \left(D(x) + k\int_{0}^{\infty} e^{-ku} D(u-x) du \right)

@@

The integral is the Laplace transform of the shifted Dawson function, with respect to $k$.  Let $v = u-x$, so that
k\int_{0}^{\infty} e^{-ku} D(u-x) du = \\ k e^{-kx} \left( \mathcal{L}\lbrace D(v) \rbrace_k - \int_0^{x} e^{kv} D(v) dv\right)
